SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-11 docs/questioning.tex
minor changes / fixes

Extensive modifications in the application's source
code can also be a reason that can make a mechanism
difficult to use. {\sc sql}rand, {\sc amnesia},
mechanisms coming from the parse-tree validation
subcategory and mechanisms coming from the taint tracking
subcategory are such examples.
In the first three cases, programmers should modify every
code fragment that involves the execution of a query.
In the latter case they should also change
all the code fragments that involve user-input handling. 
In addition, there are cases (i.e. ConScript and the system
by Phung et al.) that require many modifications
by the developers in order to introduce their policies.

Finally, even though many of the mechanism that involve
training are easy to deploy, they have a distinct disadvantage.
When the application is altered, mechanisms like {\sc sd}river
and {\sc xss-guard} require a new training phase is necessary.
However, with the increased adoption of automated testing
and continuous integration frameworks, this phase could be
easily repeated.

>>>>

Extensive modifications in the application's source
code can also be a reason that can make a mechanism
difficult to use. {\sc sql}rand, {\sc amnesia},
mechanisms coming from the parse-tree validation
subcategory and mechanisms coming from the taint
tracking subcategory are such examples.
In the first three cases, programmers should modify every
code fragment that involves the execution of a query.
In the latter case they should also change
all the code fragments that involve user-input handling.

Finally, even though many of the mechanisms that involve
training are easy to deploy, they have a distinct disadvantage.
When the application is altered, mechanisms like {\sc sd}river
and {\sc xss-guard} require a new training phase is necessary.
However, with the increased adoption of automated testing
and continuous integration frameworks, this phase could be
easily repeated.
